Developing data load and processing

### 2020-08-16 dev/data_preprocessing.Rmd
More preprocessing

```{r}
i <- 1
file_relative <- raw_data_map$File[1]
hospital_id <- raw_data_map$HospitalID[1]

@@

@@

marker_map <- c("PCR" = "pcr_value", 
                "Supp. O2" = "oxygen_flow",
                "SpO2" = "SpO2",
                "SpO2 native" = "SpO2_native",
                "Horowitz index" = "Horowitz_index",
                "PEEP" = "PEEP",
                "Ferritin" = "ferritin",
                "D-dimer" = "d_dimer",
                "CRP" = "CRP",
                "IL-6" = "IL_6",
                "Lymphocyte count" = "lymphocyte_count",
                "Hydroxychloroquine" = "hcq",
                "Azithromycin" = "az",
                "Kaletra" = "kaletra",
                "Tocilizumab" = "tocilizumab",
                "Amoxicillin/Clavulanate" = "amoxiclav",
                "Piperacilin/tazobactam" = "piperacilin_tazobactam",
                "Clarithromycin" = "clarithromycin",
                "ofloxacin" = "ofloxacin",
                "ceftriaxone" = "ceftriaxone",
                "cefuroxim" = "cefuroxim",
                "ampicillin/sulbactam" = "ampicillin_sulbactam"
                )
#Check NAs (TODO)
unrecgonized_markers <- marker_data %>% filter(!(tolower(marker) %in% tolower(names(marker_map))))

if(nrow(unrecgonized_markers) > 0) {
  print(unrecgonized_markers)
  stop("Unrecognized markers")
}

@@

#TODO - handle PCR specifically

@@

>>>>

```{r}
i <- 2
file_relative <- raw_data_map$File[i]
hospital_id <- raw_data_map$HospitalID[i]

@@

# Special handling of badly filled outcomes
if(hospital_id == "QKuFp") {
  patient_data_raw_usable <- patient_data_raw_usable %>%
    mutate(`Outcome (Discharged/Hospitalized/Transferred/Death)` =
             if_else(grepl("^439[0-9]{2}$", `Outcome (Discharged/Hospitalized/Transferred/Death)`), 
                     "Hospitalized",
                     `Outcome (Discharged/Hospitalized/Transferred/Death)`))
}

@@

marker_map <- c("PCR" = "pcr_value", 
                "Supp. O2" = "oxygen_flow",
                "SpO2" = "SpO2",
                "SpO2 native" = "SpO2_native",
                "Horowitz index" = "Horowitz_index",
                "PEEP" = "PEEP",
                "Ferritin" = "ferritin",
                "D-dimer" = "d_dimer",
                "CRP" = "CRP",
                "IL-6" = "IL_6",
                "Lymphocyte count" = "lymphocyte_count",
                "Leukocyte count" = "leukocyte_count",
                "Leukocytes" = "leukocyte_count",
                "Leukocyte" = "leukocyte_count",
                "Hydroxychloroquine" = "hcq",
                "Azithromycin" = "az",
                "Kaletra" = "kaletra",
                "Tocilizumab" = "tocilizumab",
                "Amoxicillin/Clavulanate" = "amoxiclav",
                "Piperacilin/tazobactam" = "piperacilin_tazobactam",
                "Clarithromycin" = "clarithromycin",
                "ofloxacin" = "ofloxacin",
                "ceftriaxone" = "ceftriaxone",
                "cefuroxim" = "cefuroxim",
                "cefotaxim" = "cefotaxim",
                "cefepim" = "cefepime",
                "cefepime" = "cefepime",
                "Vancomycin" = "vancomycin",
                "ampicillin/sulbactam" = "ampicillin_sulbactam",
                "zinkorot" = "zinc",
                "sulfamethoxazol" = "sulfamethoxazol",
                "trimethoprim" = "trimethoprim",
                "Meropenem" = "meropenem",
                "Fluconazol" = "fluconazol",
                "Covalescent plasma" = "convalescent_plasma",
                "Anidulafungin" = "anidulafungin"
                )
#Check NAs (TODO)
unrecgonized_markers <- marker_data %>% filter(!(tolower(marker) %in% tolower(names(marker_map))))

if(nrow(unrecgonized_markers) > 0) {
  print(unique(unrecgonized_markers$marker))
  print(unrecgonized_markers)
  stop("Unrecognized markers")
}

@@

# Special handling for PCR
pcr_data <- marker_data %>% filter(marker == "pcr_value")

pcr_values_positive <- c("pos","neg", "neg and pos", "susp.", "susp", "poz")
pcr_value_negative <- "neg"

wrong_pcr <- pcr_data %>% filter(!is.na(value),!(tolower(value) %in% pcr_values_positive), !tolower(value) %in% pcr_value_negative, !grepl("^[0-9]+$",value))
if(nrow(wrong_pcr) > 0) {
  print(wrong_pcr)
  stop("Wrong PCR")
}

pcr_data_long <- pcr_data %>% mutate(pcr_positive = as.numeric(tolower(value) %in% pcr_values_positive),
                    pcr_value = as.numeric(if_else(grepl("^[0-9]+$",value), value, NA_character_))) %>%
  select(-value, -marker) %>%
  pivot_longer(c("pcr_value","pcr_positive"), names_to = "marker", values_to = "value") %>%
  mutate(censored = "none")

# Handle NT for SpO2_native
marker_data <- marker_data %>% 
  mutate(value = if_else(marker == "SpO2_native" & value == "NT", "< 92", value) )

# Some special cases
# TODO ask at hospitel
if(hospital_id == "QKuFp") {
  marker_data <- marker_data %>% mutate(value = if_else(marker == "SpO2" & value == "NEG", NA_character_, value))
}

# Handle censoring on everything except PCR
marker_data <- marker_data %>% filter(marker != "pcr_value") %>%
  mutate(censored = case_when(startsWith(value, "<") ~ "right",
                              startsWith(value, ">") ~ "left",
                              TRUE ~ "none"),
         value_parsed = as.numeric(gsub("^[<>]? *", "", value)))

bad_parse_value <- marker_data %>% filter(is.na(value_parsed) & !is.na(value))
if(nrow(bad_parse_value) > 0) {
  print(bad_parse_value)
  stop("Bad parse value")
}

# Join with PCR data
marker_data <- marker_data %>%
  mutate(value = value_parsed) %>%
  select(-value_parsed) %>%
  rbind(pcr_data_long)

# Some special handling
if(hospital_id == "QKuFp") {
  marker_data <- marker_data %>% 
    mutate(unit = if_else(marker == "leukocyte_count" & "unit" == "unit", "10^9/l", unit))
}

@@

```{r}
# TODO check units (and convert if necessary)
marker_data %>% group_by(marker)
